### 2025-04-06 manuscript_plots/revision/extcis_current.tex
small cosmetic improvements

 &  & $\text{CRPS}^{1)}$-c & $\text{IS}_{W}^{2)}$-c & $\text{IS}_{W,b}^{2)}$-c & $\text{IS}_{U}^{2)}$-c & $\text{IS}_{50}^{2)}$-c & $\text{IS}_{80}^{2)}$-c & $\text{IS}_{\text{CISS}}^{2)}$-c & $\text{CRPS}^{1)}$-g & $\text{IS}_{W}^{2)}$-g & $\text{IS}_{W,b}^{2)}$-g & $\text{IS}_{U}^{2)}$-g & $\text{IS}_{50}^{2)}$-g & $\text{IS}_{80}^{2)}$-g & $\text{IS}_{\text{CISS}}^{2)}$-g\\

@@

 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.244 & NA & NA & NA & NA & NA & NA & 0.344\\

@@

 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & NA & NA & NA & NA & NA & NA & 0.502 & NA & NA & NA & NA & NA & NA & 0.671\\

>>>>

 &  & $\text{CRPS}^{1)}$-gg & $\text{IS}_{W}^{2)}$-gg & $\text{IS}_{W,b}^{2)}$-gg & $\text{IS}_{U}^{2)}$-gg & $\text{IS}_{50}^{2)}$-gg & $\text{IS}_{80}^{2)}$-gg & $\text{IS}_{\text{CISS}}^{2)}$-gg & $\text{CRPS}^{1)}$-cc & $\text{IS}_{W}^{2)}$-cc & $\text{IS}_{W,b}^{2)}$-cc & $\text{IS}_{U}^{2)}$-cc & $\text{IS}_{50}^{2)}$-cc & $\text{IS}_{80}^{2)}$-cc & $\text{IS}_{\text{CISS}}^{2)}$-cc\\

@@

 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 0.244 & -- & -- & -- & -- & -- & -- & 0.344\\

@@

 & Direct$^{4)}$: BVAR-CISS$^{3)}$ & -- & -- & -- & -- & -- & -- & 0.502 & -- & -- & -- & -- & -- & -- & 0.671\\
